### 2015-07-08 2015-compmorphon-morphver/poster.tex
one more step(!): compile
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61222 72bbbca6-d526-0410-a7d9-f06f51895060
stretch flow chart vertically
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61223 72bbbca6-d526-0410-a7d9-f06f51895060
smoe more space adjustments
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61224 72bbbca6-d526-0410-a7d9-f06f51895060

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			%\scalebox{0.8}{
			%\begin{tikzpicture}[node distance = 2cm, auto]
			%	% Place nodes
			%	\node [cloud, above of=fixphon] (assumed) at (5.5,1.5) {assumed phonology} ;
			%	\node [block] (init) at (1,3) {analyse corpus} ;
			%	\node [block, left of=init] (addstem) at (0,3) {add stem};
			%	\node [block, right of=init] (fixphon) at (3.5,3) {fix phonology};
			%	\node [block, below of=init] (freq) at (1,2) {examine frequency list};
			%	\node [decision, right of=freq] (break) at (1.5,0) {did something break?};
			%	%\node [block, below of=identify] (evaluate) {evaluate candidate models};
			%	%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
			%	\node [decision, below right of=freq] (decide) at (0,-1) {cause for unanalysed forms?};
			%	\node [cloud] (revised) at (6.75,-4.5) {revised phonology} ;
			%	%\node [block, below of=decide, node distance=3cm] (stop) {stop};
			%	% Draw edges
			%	\path [line] (init) -- (freq);
			%	\path [line] (freq) -- (break);
			%	\path [line] (break.south) -| node [near start] {no} (decide.north) ;
			%	\path [line] (break.north) -| node [near start] {yes}(fixphon.south) ;
			%	\path [line] (decide) -| node [near start] {missing stem} (addstem);
			%	\path [line] (decide.east) --(decide-|fixphon.east) node [below, midway] {bad phonology} |-(break.north-|fixphon.south) -- (fixphon.south);
			%	\path [line] (addstem) -- (init);
			%	\path [line] (fixphon) -- (init);
			%	\path [line,dashed] (assumed) -- (fixphon);
			%	\path [line,dashed] (fixphon.east) --(fixphon.east-|assumed.east) |-(decide.east-|revised.north) -- (revised.north);
			%\scalebox{0.65}{
			\begin{tikzpicture}[xscale=1.92,yscale=2.25]%, auto]

				\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
				\node[block] (analyse) at (1,2) {analyse corpus};
				\node[block] (check) at (1,1) {examine freq.\ list};
				\node[decision] (missingstem) at (1,0) {missing stem?};
				\node[block] (addstem) at (0,2) {add stem};
				\node[decision] (phonormorph) at (2,0) {type of problem?};
				\node[block] (updatephon) at (3,0) {update phonol.};
				\node[block] (updatemorph) at (3,1) {update morphol.};
				\node[decision] (phonbetter) at( 4,0) {better?};
				\node[decision] (morphbetter) at (4,1) {better?};
				\node[cloud] (newgeneralisation) at (2.5,2) {new\\grammatical\\generalisation};

				\path[line] (assumptions) -- (analyse);
				\path[line] (analyse) -- (check);
				\path[line] (check) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (missingstem);
				\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
				\path[line] (addstem) -- (analyse);
				\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
				\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
				\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
				\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (phonbetter) ;
				\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (morphbetter) ;
				\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.5,0) |- (newgeneralisation.east) ;
				\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.5,1) |- (newgeneralisation.east) ;
				\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,0.5) -| (updatephon.north) ;
				\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,1.5) -| (updatemorph.north) ;
				\path[line] (newgeneralisation) -- (analyse);

>>>>

		\headerbox{Development cycle}{name=development,below=morphtrans}{
			%(1) look at frequency list --> check word --> if it's missing stem, add --> (1) ; if it's bad phonology --> fix phonology --> (1)
			%\scalebox{0.8}{
			%\begin{tikzpicture}[node distance = 2cm, auto]
			%	% Place nodes
			%	\node [cloud, above of=fixphon] (assumed) at (5.5,1.5) {assumed phonology} ;
			%	\node [block] (init) at (1,3) {analyse corpus} ;
			%	\node [block, left of=init] (addstem) at (0,3) {add stem};
			%	\node [block, right of=init] (fixphon) at (3.5,3) {fix phonology};
			%	\node [block, below of=init] (freq) at (1,2) {examine frequency list};
			%	\node [decision, right of=freq] (break) at (1.5,0) {did something break?};
			%	%\node [block, below of=identify] (evaluate) {evaluate candidate models};
			%	%\node [block, left of=evaluate, node distance=3cm] (update) {update model};
			%	\node [decision, below right of=freq] (decide) at (0,-1) {cause for unanalysed forms?};
			%	\node [cloud] (revised) at (6.75,-4.5) {revised phonology} ;
			%	%\node [block, below of=decide, node distance=3cm] (stop) {stop};
			%	% Draw edges
			%	\path [line] (init) -- (freq);
			%	\path [line] (freq) -- (break);
			%	\path [line] (break.south) -| node [near start] {no} (decide.north) ;
			%	\path [line] (break.north) -| node [near start] {yes}(fixphon.south) ;
			%	\path [line] (decide) -| node [near start] {missing stem} (addstem);
			%	\path [line] (decide.east) --(decide-|fixphon.east) node [below, midway] {bad phonology} |-(break.north-|fixphon.south) -- (fixphon.south);
			%	\path [line] (addstem) -- (init);
			%	\path [line] (fixphon) -- (init);
			%	\path [line,dashed] (assumed) -- (fixphon);
			%	\path [line,dashed] (fixphon.east) --(fixphon.east-|assumed.east) |-(decide.east-|revised.north) -- (revised.north);
			%\scalebox{0.65}{
			\begin{tikzpicture}[xscale=1.92,yscale=2.65]%, auto]

				\node[cloud] (assumptions) at (1,2.75) {assumed generalisations};
				\node[block] (compile) at (1,2) {compile analyser};
				\node[block] (analyse) at (1,1.5) {analyse corpus};
				\node[block] (check) at (1,1) {examine freq.\ list};
				\node[decision] (missingstem) at (1,0) {missing stem?};
				\node[block] (addstem) at (0.22,2) {add stem};
				\node[decision] (phonormorph) at (2,0) {type of problem?};
				\node[block] (updatephon) at (3,0) {update phonol.};
				\node[block] (updatemorph) at (3,1) {update morphol.};
				\node[decision] (phonbetter) at( 4,0) {better?};
				\node[decision] (morphbetter) at (4,1) {better?};
				\node[cloud] (newgeneralisation) at (2.5,2) {new\\grammatical\\generalisation};

				\path[line] (assumptions) -- (compile);
				\path[line] (compile) -- (analyse);
				\path[line] (analyse) -- (check);
				\path[line] (check) -- node [right=0.75ex, scale=\flowchartscale, align=left] {unanalysed\\forms} (missingstem);
				\path[line] (missingstem) -| node [below=1ex, near start, scale=\flowchartscale] {yes} (addstem);
				\path[line] (addstem) -- (compile);
				\path[line] (missingstem) -- node [below=1ex, midway, scale=\flowchartscale] {no} (phonormorph);
				\path[line] (phonormorph) -- node [below=1ex, near start, scale=\flowchartscale] {phon} (updatephon);
				\path[line] (phonormorph) |- node [below=1ex, near end, scale=\flowchartscale] {morph} (updatemorph);
				\path[line] (updatephon) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (phonbetter) ;
				\path[line] (updatemorph) -- node [above=0.5ex, scale=\flowchartscale, align=center] {diff \\ freq \\ list} (morphbetter) ;
				\path[line] (phonbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,0) |- (newgeneralisation.east) ;
				\path[line] (morphbetter.east) -- node [below=1ex, near start, scale=\flowchartscale] {yes} (4.6,1) |- (newgeneralisation.east) ;
				\path[line] (phonbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,0.5) -| (updatephon.north) ;
				\path[line] (morphbetter.north) |- node [right=1ex, near start, scale=\flowchartscale] {no} (4,1.5) -| (updatemorph.north) ;
				\path[line] (newgeneralisation) -- (compile);
